\documentclass{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{listings}
\usepackage{float}
\title{MPC in Practice Research Plan}
\author{Tianxing Wu}

\begin{document}
\maketitle

\section{Research Purpose}
The purpose of this research is to explore and understand the compatibility between various message-passing frameworks, such as the k-machine model, congested clique, and BSP, and different distributed computing frameworks, including MPI, OpenMP, Pytorch, and TensorFlow.

Evaluation of Compatibility/Incompatibility:
\begin{enumerate}
  \item{
    Evaluating Performance:
      \begin{itemize}
        \item How does this framework perform in comparison to another framework with the same message-passing model and problem, in terms of communication rounds and memory usage?
        \item How does this framework's performance change if the problem scales, in terms of strong scaling and weak scaling?
      \end{itemize}
    }
  \item {
    System Requirements from the Programming Framework:
      \begin{itemize}
        \item Memory usage
        \item CPU usage
        \item Network bandwidth
        \item Disk I/O
      \end{itemize}
    }
\end{enumerate}

\section{Objective}
For a specific framework and model, the objective is to demonstrate one of the following:
\begin{itemize}
  \item The framework and model are perfectly compatible.
  \item The framework and model are not perfectly compatible, but with some additional effort, they could work together efficiently to solve problems.
  \item The framework and model are completely incompatible.
\end{itemize}
To demonstrate compatibility, algorithms will be presented with accompanying proofs. To indicate incompatibility, proofs will also be required.

\section{Method}
\begin{itemize}
  \item Reviewing and understanding the documentation of programming frameworks.
  \item Analyzing the compatibility of frameworks and models:
      \begin{enumerate}
        \item Selecting classical problems that require High-Performance Computing (HPC), such as graph problems.
        \item Designing algorithms using the selected frameworks and models.
        \item Analyzing performance in terms of time and memory usage, considering scalability.
        \item Concluding the compatibility between a specific model and a framework.
        \item (Optional) Applying the algorithm on real machines to verify the results.
      \end{enumerate}
\end{itemize}

\section{Plan}
The duration of this research is planned for 6 months.

Month 1 - 2:
\begin{itemize}
  \item Literature Review. Conduct a comprehensive review of existing studies on MPI, OpenMP, PyTorch, TensorFlow, and message-passing models like the k-machine model, congested clique, and BSP.
  \item Selecting problems for analysis.
  \item Design a metric for evaluating the performance.
\end{itemize}

Months 3 - 4:
\begin{itemize}
  \item Designing algorithms concerning the frameworks and models, analyzing the performance, and evaluating using the metrics.
\end{itemize}

Months 5 - 6:
\begin{itemize}
  \item Writing the research report.
\end{itemize}

Optional:
\begin{itemize}
  \item Applying the algorithms on real machines to verify the results.
\end{itemize}

\section{Reference}
\begin{itemize}
  \item J. Augustine, K. Kothapalli and G. Pandurangan, "Efficient Distributed Algorithms in the k-machine model via PRAM Simulations," 2021 IEEE International Parallel and Distributed Processing Symposium (IPDPS), Portland, OR, USA, 2021, pp. 223-232, doi: 10.1109/IPDPS49936.2021.00031.
  \item John Augustine, Mohsen Ghaffari, Robert Gmyr, Kristian Hinnenthal, Fabian Kuhn, Jason Li, and Christian Scheideler. Distributed Computation in the Node-Congested Clique. arXiv preprint arXiv:1805.07294v1, 2018.
  \item John Augustine, Mohsen Ghaffari, Robert Gmyr, Kristian Hinnenthal, Fabian Kuhn, Jason Li, and Christian Scheideler. Distributed Computation in the Node-Congested Clique. arXiv preprint arXiv:1805.07294v1, 2018.
  \item Arvind Krishnamurthy and John Zahorjan. Parallel Algorithms. University of Washington, 2002.
  \item Martín Abadi et al. TensorFlow: Large-Scale Machine Learning on Heterogeneous Systems. 2015.
  \item Message Passing Interface Forum. MPI: A Message-Passing Interface Standard Version 3.1. 2015.
  \item Dagum, Leonardo, and Ramesh Menon. “OpenMP: an industry standard API for shared-memory programming.” Computational Science & Engineering, IEEE 5.1 (1998): 46-55.

  
\end{itemize}

\end{document}